Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-11-08 RMS/final-version/ALL_15-TIE-3480.tex
renamed the photos

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Jiaxiang_Liu.jpeg}}]%
{Jiaxiang Liu} received his B.S.\ degree in software engineering from
Tsinghua University, Beijing, China in 2010. Since 2010, he has been
working toward the Ph.D.\ degree in computer science at the Department
of Computer Science and Technology, Tsinghua University, Beijing,
China.

@@

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Min_Zhou.jpeg}}]%
{Min Zhou} received his B.S.\ degree in mathematics, and the
Ph.D.\ degree in computer science from Tsinghua University, Beijing,
China in 2007 and 2014, respectively.

@@

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Xiaoyu_Song.jpeg}}]%
{Xiaoyu Song} received the Ph.D.\ degree from the University of Pisa,
Italy, in 1991. From 1992 to 1998, he was on the faculty at the
University of Montreal, Canada. He joined the Department of Electrical
and Computer Engineering at Portland State University in 1998, where
he is now a professor. He was an editor of IEEE Transactions on VLSI
Systems and IEEE Transactions on Circuits and Systems. He was awarded
an Intel Faculty Fellowship from 2000 to 2005. His research interests
include formal methods, design automation, embedded systems and
emerging technologies.
\end{IEEEbiography}

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Ming_Gu.jpeg}}]%
{Ming Gu} received the B.S.\ degree in computer science from the
National University of Defense Technology, China in 1984, and the
M.S.\ degree in computer science from the Chinese Academy of Science,
China in 1986.

@@

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Jiaguang_Sun.jpeg}}]%
{Jiaguang Sun} received the B.S.\ degree in automation science from
Tsinghua University, China in 1970.

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_JIAXIANG_LIU.jpeg}}]%
{Jiaxiang Liu} received his B.S.\ degree in software engineering from
Tsinghua University, Beijing, China in 2010. Since 2010, he has been
working toward the Ph.D.\ degree in computer science at the Department
of Computer Science and Technology, Tsinghua University, Beijing,
China.

@@

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_MIN_ZHOU.jpeg}}]%
{Min Zhou} received his B.S.\ degree in mathematics, and the
Ph.D.\ degree in computer science from Tsinghua University, Beijing,
China in 2007 and 2014, respectively.

@@

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_XIAOYU_SONG.jpeg}}]%
{Xiaoyu Song} received the Ph.D.\ degree from the University of Pisa,
Italy, in 1991. From 1992 to 1998, he was on the faculty at the
University of Montreal, Canada. He joined the Department of Electrical
and Computer Engineering at Portland State University in 1998, where
he is now a professor. He was an editor of IEEE Transactions on VLSI
Systems and IEEE Transactions on Circuits and Systems. He was awarded
an Intel Faculty Fellowship from 2000 to 2005. His research interests
include formal methods, design automation, embedded systems and
emerging technologies.
\end{IEEEbiography}

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_MING_GU.jpeg}}]%
{Ming Gu} received the B.S.\ degree in computer science from the
National University of Defense Technology, China in 1984, and the
M.S.\ degree in computer science from the Chinese Academy of Science,
China in 1986.

@@

\vspace{-5mm}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_JIAGUANG_SUN.jpeg}}]%
{Jiaguang Sun} received the B.S.\ degree in automation science from
Tsinghua University, China in 1970.
